\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Igmar}
\familyname{Palsenberg}
\address{Eltingerhof 90}{6921 DG}
\phone[mobile]{+31 613256781}
\title{Curriculum Vitae}
\email{igmar@palsenberg.com}
\homepage{www.palsenberg.com}
\social[twitter]{Palsenberg}
\social[github]{igmar}
\social[linkedin]{igmarpalsenberg}
\social[skype]{igmarpalsenberg}
\social[stackoverflow]{2378559}
\extrainfo{Dutch drivers license B}
%% \quote{``Quality over quantity.''}

%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{1997--2001}{Bsc in Information Techologie}{HAN univeristy of applied science}{}{Bsc}{}
\cventry{1993--1997}{Telematics}{MTS Deventer}{}{}{}

\section{Languages}
\cvitemwithcomment{Dutch}{Native language}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{German}{Good}{}

\section{Bachelor thesis}
\cventry{2001--2001}
{Thesis}
{C, PHP}
{Graduate project}{}
{
Wrote an PostgreSQL extension that encrypts the database records in a row
level. The extensions comes with some options that make storing transactional
data in PostgreSQL easier.
}

\section{Internship}
\cventry{2000}{End-year internship at Tunix}{}{}{}{Designed and implemented a firewall log analysis system}

\section{Community}
\cventry{Blog}{\url{www.palsenberg.com}}{My blog}{}{}{}
\cventry{Github}{\url{github.com/igmar}}{Github}{}{}{}
\cventry{Tweakers.net}{\url{http://tweakers.net/gallery/5365}}{}{}{}{}

\section{Work Experience}
%% \subsection{Research Projects}

\vspace*{0.2\baselineskip}
\cventry{2020-}
{Platform Architect}
{ING}
{Amsterdam}
{}
{
  Platform architect, focussed on reactive technologies
  and infra components.
  I actively promote reactive designs based on the reactive
  manifesto, with a strong focus on Akka, Akka Cluster and Akka Streams.
  I'm a specialist in middleware technologies (databases, messaging
  services, streaming data platforms), providing design guidance to
  teams and help on the implementation side.
}

\cventry{2018-2020}
{IT Chapterlead}
{ING}
{Amsterdam}
{}
{
    Leading a team of 15 engineers. The focus is on creating and developing
    a team of great engineers, both onshore as well as offshore.
}

\cventry{2017-}
{Dev Engineer}
{ING}
{Amsterdam}
{}
{
    Dev Engineer working on ING's next generation payment engine. 
    The implementation is fully reactive, written using Akka,
    Akka streams and Alpakka.
    We're migrating legacy systems to a scalable, multinode payment
    engine, designed to do realtime payment for both internal and
    external customers.
    \newline{}%
    Detailed achievements:%
    \begin{itemize}
        \item Helping create the foundations of the new payment engine.
        \item Designing ING's new Clearing and Settlement hub.
        \item Bringing the new CSH to production
    \end{itemize}
}

\cventry{2014--2017}
{Software architect}
{Coolgames}
{Amsterdam}
{}
{
    Tech lead and architect, re-designing and expanding our microservices
    architecture. We develop using Play Framework 2.x and Java 8 exclusively.
    I develop with scalability in mind, in order to serve all traffic
    requirements needed. We do this based on a message drive reactive
    application stack, developed in Play, using Akka cluster technology.
    \newline{}%
    Detailed achievements:%
    \begin{itemize}
        \item Migrated from a monolith application in Spring and Play 1 to microservices using Play 2
    \end{itemize}
    Achieved goals:%
    \begin{itemize}
        \item Create a resilient platform that is self-scaling and self-healing
        \item Improve overall quality
        \item Automate deployments
    \end{itemize}
}

\cventry{2013--2014}
{Senior JAVA backend developer}
{Coolgames}
{Amsterdam}
{}
{
    Member of the backend team, implementating backend services using using Play framework 1.x and 2.x.
    The backend services are used to service high-traffic gaming websites. The backend is based 
    in microservices, and deployed in Amazon AWS.
    We develop either in Java 7 or Java 8, using the reactive manifesto philosophy.\newline{}%
    \newline{}%
    Detailed achievements:%
    \begin{itemize}
        \item Introduced Play framework 2, to bring the stack to today's standards
        \item Introduced proper DevOps operations, fulling automating building and deploying applications
    \end{itemize}
}

\vspace*{0.2\baselineskip}
\cventry{2001--2013}
{Lead developer}
{JDI ICT}
{Arnhem}
{}
{
    Lead developer of JDI ICT. I was responsible for all technical decisions made within the company.
    We created our own CMS in 2003, aimed that time at the best customer experience, written in LAMP.
    We rewrote the CMS in 2013 using the latest technologies, using Play 1 and React, but keeping the focus aimed at the customer experience.
    \newline{}%
    Daily tasks:%
    \begin{itemize}
        \item Leading troubleshooter
        \item Leading research, and writing proposals based on that
        \item Server maintenance, both internal and external
        \item Leading finance
    \end{itemize}
}

\section{Skills}
\cventry{Languages}{C = Java  > C++ > Bash > Python}{}{}{}{}
\cventry{Cloud}{AWS}{}{}{}{}
\cventry{Atlassian}{JIRA, Confluence, Bamboo, Stash}{}{}{}{}
\cventry{Version control}{Git}{}{}{}{}
\cventry{Linux}{CentOS, RHEV}{}{}{}{}
\cventry{Frameworks}{Akka, Akka Streams, Alpakka, Play framework}{}{}{}{}
\cventry{Big Data}{Cassandra, DynamoDB}{}{}{}{}
\cventry{Payments}{PACS008,Equens,EBA,International payments}{}{}{}{}
\cventry{Games}{OceanHorn, Insurgency}{}{}{}{}
\end{document}
